Weather Data Integration and Assimilation System\\

### 2020-02-11 thesis.tex
Misc fixes on references
Added appendix
Removed appendix
After 2nd review

\acrfull{nwm} utilize data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images. Prior to using such multimodal data into respective \acrshort{nwm}, it is necessary to transcode into a format that can be ingested by the \acrshort{nwm} modal. Moreover, the data integration system's response time needs to be relatively low to forecast and monitor time-sensitive weather events like hurricanes, storms, and flash floods that require rapid and frequent execution of \acrshort{nwm}. Later such weather data needs to be accessed by many third-party applications and research in order to make use of them. Thus the system should provide easy protocol to integrate with external systems, and should be capable of handling the workload. For example, logistic companies could use those data within their models to plan and schedule deliveries. Agricultural insurance companies can warn the farmers in advance, as well as calculate premiums based on anticipated weather patterns.

Even though there are many data integration systems, most of them are proprietary or close sourced. Which means for an island like Sri Lanka that having different kinds of weather seasons over the year than those software originated need to be highly customized. Throughout the operations and maintenance, it is required to get support with paying lots of charges, and difficult to debug into a closed source system without maintenance support from the vendors. And most of the software existing out there is not up to date with the latest technology concepts such as Cloud Computing. \acrfull{wdias} uses the modern architecture pattern such as microservice in order to achieve scalability, rather using monolithic architecture or client service architecture.

It provides a modular approach to integration of data from different sources and export into different formats, and inbuilt extension module system allow users to add new features. Since each module follows the stateless and failover microservice integrate with new Cloud Computing tools, the proposed solution comes with the scalability and high availability into large extend out of the box. The proposed solution is independent of the platform which most software out there is not and independent of Cloud Platform providers which give much flexibility for the users to decide the best cost effective way to host it. And the auto scaling feature allows users to run \acrshort{wdias} from 1 CPU node to nodes with a few hundred CPUs. Unlike most existing systems \acrshort{wdias} does not require a shutdown in order to update the system configuration, and it allows to add new features on the fly with rollover capabilities.

\vspace{4mm}

\textbf{Keywords:} Cloud Computing, Data Management system, Distributed,  Highly Available, Scalable, Timeseries, Weather
}
\restoregeometry
\normalsize

@@

@@

\addcontentsline{toc}{chapter}{List of Abbreviations} 
\printglossary[style=custom-glossary-style, type=\acronymtype, title=List of Abbreviations, toctitle=List of Abbreviations, nonumberlist]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Introduction}
\label{ch:intro}
\pagenumbering{arabic}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix
\chapter{First Appendix}
Type out your first appendix here.
\section{Basics}

\chapter{First Appendix}
Type out your second appendix here.

>>>>

\acrfull{nwm} utilize data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images. Before using such multimodal data into a NWM, it is necessary to transcode data into a format that can be ingested by the NWM. Moreover, the data integration system's response time needs to be relatively low to forecast and monitor time-sensitive weather events like hurricanes, storms, and flash floods that require rapid and frequent execution of \acrshort{nwm}. The resulting weather data also need to be accessed by many researchers and third-party applications such as logistic companies and agricultural insurance. %Thus, the system should provide a simple protocol to integrate with external systems.
%For example, logistic companies could use those data within their models to plan and schedule deliveries. Agricultural insurance companies can warn the farmers in advance, as well as calculate premiums based on anticipated weather patterns.
Even though there are several weather data integration systems, they are based on monolithic or client-server architectures and are unable to benefit from novel computational models such as cloud computing and containers. Moreover, most of this software is proprietary or closed sourced; hence, it is difficult to customize such software for an island like Sri Lanka with different weather seasons. %than those software originated need to be highly customized. Throughout the operations and maintenance, it is required to get support with paying lots of charges, and difficult to debug into a closed source system without maintenance support from the vendors. And most of the software existing out there is not up to date with the latest technology concepts such as Cloud Computing. 
\db{Therefore, in this research, we propose \acrfull{wdias} that utilizes modern architecture pattern such as microservices to achieve scalability, high availability, and low-cost operation based on cloud computing. \acrshort{wdias} provides a modular architecture to integrate data from different sources, export into different formats, and the inbuilt extension module system allow users to add new features. Due to the use of stateless microservices, \acrshort{wdias} achieves high scalability, availability, and enables the addition of new features on the fly with rollover capabilities. We demonstrate the utility of \acrshort{wdias} using cloud-based experimental setup and weather-related synthetic workloads.}
%Because each module follows the stateless and failover microservices integrate with new Cloud Computing tools, the proposed solution comes with the scalability and high availability into large extend out of the box. The proposed solution is independent of the cloud platform which most software out there is not and independent of Cloud Platform providers which give much flexibility for the users to decide the best cost effective way to host it. And the auto scaling feature allows users to run \acrshort{wdias} from 1 CPU node to nodes with a few hundred CPUs. Unlike most existing systems \acrshort{wdias} does not require a shutdown in order to update the system configuration, and it allows to add new features on the fly with rollover capabilities.

\dbc{Increase line space to 1.5}
\vspace{4mm}

\textbf{Keywords:} Cloud computing, \db{data assimilation, data integration, hierarchical databases, microservice, weather}
%Cloud Computing, Data Management system, Distributed,  Highly Available, Scalable, Timeseries, Weather
}
\restoregeometry
\normalsize

@@

\dbc{Need to ACK CUrW for grant.}

@@

\addcontentsline{toc}{chapter}{List of Abbreviations} 
\printglossary[style=custom-glossary-style, type=\acronymtype, title=List of Abbreviations, toctitle=List of Abbreviations, nonumberlist]
\dbc{Make sure line spacing is consistent here.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Introduction}
\label{ch:intro}
\pagenumbering{arabic}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \appendix
% \import{Appendix/}{app_1_soa_and_actor_model.tex}
